---
title: "example PlotFuncs"
author: "AlexGu at Lund University"
date: "`r Sys.Date()`"
output:
  rmdformats::readthedown:
    self_contained: true
    thumbnails: true
    lightbox: true
    gallery: false
    highlight: tango
---

```{r setup, include=FALSE}
options(warn=-1)
knitr::opts_chunk$set(echo = TRUE)

```

This tutorial will use the <b><big>Language_based_assessment_data_8</big></b> in Text package to generate a plot.

# Import packages and functions

```{r import the plotting functions, echo=TRUE}

if (FALSE){
  # install packages needed for punctuation restoring. In a future Text version, this is not necessary.
  reticulate::conda_install(envname="textrpp_condaenv", c("protobuf","sentencepiece"), forge=FALSE, pip=TRUE)
}

library(tidyverse)
library(text)

reticulate::source_python("fullStopCorrt_copy.py")
source(
  "textPlotText_v0.2.R", # plotting functions
  encoding=localeToCharset()
)

# supported models: bert, roberta base models
nameLLM <- "bert-base-uncased"
tokenizers <- getTokenizer(nameLLM)
```

# Import data

```{r data import, echo=TRUE}
data <- Language_based_assessment_data_8
print(nrow(data)) # 40 records
```
# Restore punctuations 

```{r restore punctuations, echo=TRUE}
# Choose harmonytexts as the visualization target in this example.

data <- data[,c("harmonytexts", "hilstotal")]

# Only needed if one finds the missing of puncuations in the text. 
# !!!! After running this code, a restart of the R console is needed. Plan to fix in the future.
if (FALSE){
  data[,"harmonytexts"] <- sentsMarker(data[,"harmonytexts"])
  .rs.restartR()
}

```

# Get embeddings

```{r get embed, echo=TRUE}
embed1 <- textEmbed(
                    data[2:40, "harmonytexts"],
                    model=nameLLM,
                    device = "mps", # cpu, gpu, mps
                    dim_name = FALSE # For prediction of new texts, this param must be FALSE
)
```
# Separate sentences

```{r Separate sents, echo=TRUE}

toTrain <- token2Sent(embed1, tokenizers, nameLLM,
                      include_CLS_SEP="both" # Keep the CLS and SEP special token as well.
)
```


# Train a model to predict the target

```{r regression, echo=TRUE}

theModels <- langTrain(toTrain, # embedding
           data[2:40, "hilstotal"], # scale values, target
                   "all", # options: "token", "sentence", "passage", "all", # "all" include all the previous models
                   tokenizers,
                   modelName = nameLLM
                   )
```

```{r save the regression model, echo=TRUE}
# Save the models for future use since the training is a bit slow.
saveRDS(theModels, paste0("model.rds"))
#theModels <- readRDS("model.rds")
```

# Use the model to predict new texts

```{r Get embed of pred texts and predict, echo=TRUE}
toPredEmbed <- textEmbed(data[1,"harmonytexts"],
                         model=nameLLM,
    dim_name=FALSE, device="mps")
```


# Plot preparation

```{r Plot_preparation, echo=TRUE}
toPred <- token2Sent(toPredEmbed, tokenizers, nameLLM, include_CLS_SEP="both")
output <- langPred(toPred, theModels, "all", tokenizers, nameLLM)
output <- list("Pred" = output, "model" = theModels)
output <- getLangColorTb(output)
toPlot <- getOutDf(output, nameLLM)

```

# Plot the default plot

```{r Plot, echo=TRUE}

plot1 <- textPlotText(toPlot, list("all"), textColor="black", modelName=nameLLM)

plot1

```

# Custom the color of the plot

```{r Change the color of the plot, echo=TRUE}
cusColVecRGB <- list(list(10,50,100), list(130, 180, 230)) # 0-255; from lower to higher
# Default list(list(243,249,246), list(253, 247, 244)) 

toPlot_cusRGB <- cusPlotText(toPlot, cusColVecRGB, "RGB", restore=FALSE, nameLLM)

plot2 <- textPlotText(toPlot_cusRGB, list("all"), textColor="black", modelName=nameLLM)

plot2
```

# Restore the plot to the default color

```{r Restore the color to default, echo=TRUE}
toPlot_ori <- cusPlotText(toPlot_cusRGB, restore=TRUE, modelName=nameLLM)

plot3 <- textPlotText(toPlot_ori, list("all"), textColor="black", modelName=nameLLM)

plot3

```